---
title: "semi_simulation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r pacakges}
library(MASS)
library(Iso)
library(mvtnorm)
```
## Model overview
### Basic model
Recently Wang and Zhou (2018) proposed a parametric transformation model for biomarker data, of the form
$$ f(\mathbf{t}|\mathbf{x},\mathbf{z}) = \sum_{d=0}^{L-1}\pi_d(\mathbf{z})\prod_{k=1}^KJ(t_k,\lambda_k)g(H_k(t_k,\lambda_k|\mathbf{x}), $$
where $g(\cdot|\mathbf{x})$ is a known parametric density, $H(\cdot,\cdot)$ is a given transformation, $J(t_k,\lambda_k)$ is the transformation Jacobian, and $\pi_d(\mathbf{z})$ is the mixture proportion, which is specified as a logit form. In their model, the joint
density is independent given the covariate $\mathbf{x}$

### Our extension
Here our model is more general, the joint density is not independent, and the monotone transformations $H_k(\cdot)$'s are also unknown to be estimated
The observed data is $D_n=\{ (\mathbf{y}_i,\mathbf{x}_i)\}: i=1,...,n\}$ from $n$ subjects. $\mathbf{y}_i=(y_{i1},...,y_{ik})^T$ is the observation of the $i$-th subject with k biomarkers, $\mathbf{x}_i = (x_{i1},...,x_{iq})$ is the corresponding covariates, we assume the $(\mathbf{y}_i,\mathbf{x}_i)$'s are iid. 

The goal is to classify
each subject to one of the two groups, normal and disabled. For this, we first need to specify a model, then estimate the model parameters and finally, classify the subjects.

The normal model is easy to use but not robust to model assumption. For robustness we  propose the following semi-parametric transformation model for the observed data. First, for each margin, we specify the transformation
$$g_j(y_{ij}) =\mathbf{x}^T_i\mathbf{\beta}_{j}+\epsilon_{ij}~~~~~~( i=1,2,...,n; j=1,...,k) (1)$$
where  $g_j(\cdot) \in {\cal G}$, ${\cal G}$  is the collection of  bounded monotone non-decreasing functions, and $\epsilon_{ij}$ is the noise. We assume  $\mathbf{\epsilon}_i:=(\epsilon_{i1},...,\epsilon_{ik})^T \sim N(\mathbf{0},\Omega)$, $\Omega=(\omega_{ij})_{k\times k}$. Denote $\mathbf{g}(\mathbf{y}_i)= \big(g_1(y_{i1}),...,g_k(y_{ik})\big)^T$ and $\mathbf{x_i}=(x_{i1},...,x_{iq})^T$, $\mathbf{beta}_j=(\beta_{j1},...,\beta_{jq})^T$ and $\mathbf{B}^T=(\mathbf{\beta}_1,...,\mathbf{\beta}_k)$. Let $\phi(\cdot|\Omega)$ be the density function of the $N(\mathbf{0},\Omega)$ distribution. Next, since the group status of each subject is unknown, the joint model is specified as a mixture
$$ f(\mathbf{y}_i|\mathbf{x}_i) = \sum_{d=0}^1\pi_d(\mathbf{x}_i)\phi(\mathbf{g}(\mathbf{y}_i)-\mathbf{x}^T_i\mathbf{B}|\Omega) (2) $$
where
$$ \pi_0(\mathbf{x}_i|\mathbf{\eta})=1-\pi_1(\mathbf{x_i}|\mathbf{\eta})=\frac{\exp(\mathbf{x}_i^T\mathbf{\eta})}{1+\exp(\mathbf{x}_i^T\mathbf{\eta})}$$
is the mixing proportions. $\pi_d(\mathbf{x}_i|\mathbf{\eta})$ is the probability subject $i$ belongs to group $d$.



## Simulation settings:
* Assumption1: joint density is not independent, 
and $H_k(\cdot)$  = $I_k(\cdot)$, $k = 2$ (2 biomarkers) with $q = 2$ (2 covariates).

We need to estimate $\mathbf{\eta} = \{\eta_1,\eta_2,...,\eta_q\}$, $\mathbf{\theta}=\{\mathbf{\eta}_{jd},~\omega_{jr}: j,r=1,...,k; d=0,1\}$ and $\mathbf{g}(\cdot)=(g_1(\cdot),...,g_k(\cdot))$. Note that since the $\omega_{jr}$'s are symmetric, we only need to estimate $\omega_{jr}$ for $j=1,...,k; r\geq j$.  Let $\delta_i$ be the latent group indicator of the $i$-th subject, $\delta_i=0$ if this subject belongs to group 0, and $\delta_i=1$ otherwise. Let $D_{n,c}=\{ (\mathbf{y}_i,x_i,\delta_i): i=1,...,n\}$  be the ``complete'' data. The log-likelihood of the complete data is
$$ \ell(\mathbf{\eta},\mathbf{\theta},\mathbf{g}|D_{n,c}) = \sum_{i=1}^n \sum_{d=0}^{1}\Big[I_d(C_i)\Big(\log\pi_d(\mathbf{x}_i|\mathbf{\eta})-\frac{1}{2}\big(\mathbf{g}(\mathbf{y}_i)-\mathbf{x}^T_i\mathbf{B})^T\Omega^{-1}\big(\mathbf{g}(\mathbf{y}_i)-\mathbf{x}^T_i\mathbf{B}\big)\Big)$$ 
$$-\frac{n}{2}\log |\Omega|.(3)$$
We estimate $(\mathbf{\eta},\mathbf{\theta},\mathbf{g})$ by
$$ (\hat{\mathbf{\eta}},\hat{\mathbf{\theta}},\hat{\mathbf{g}})= \arg\max_{(\mathbf{\eta},\mathbf{\theta},\mathbf{g})\in(\mathbf{B}, \mathbf{\Theta},{\cal G}^k)}\ell(\mathbf{
\eta},\mathbf{\theta},\mathbf{g}|D_{n,c}) .(4)$$


* Simulation1






<!-- ## Initial values: -->
<!-- ```{r initial} -->
<!-- k <-2; #number of biomarker -->
<!-- m <-2; #covariates dimension -->
<!-- d <-2; #number of class -->
<!-- set.seed(123) -->
<!-- N<- 1000 #number of observation -->

<!-- ## B -->
<!-- beta1 <- c(0.1,0.3) -->
<!-- beta2 <- c(0.2,0.4) -->
<!-- B.0 <- matrix(c(beta1,beta2),2) -->

<!-- beta1 <- c(-0.1,0.2) -->
<!-- beta2 <- c(-0.2,0.3) -->
<!-- B.1 <- matrix(c(beta1,beta2),2) -->

<!-- # B.1 = B.0 -->

<!-- ## Delta -->
<!-- # delta <- sample(c(0,1),N, replace = T) -->


<!-- ## X -->
<!-- x1 = rnorm(N,0,1) -->
<!-- x2 = rnorm(N,0,2) -->
<!-- X = data.frame(x1 = x1, x2 = x2) -->

<!-- ## g.y -->
<!-- eta<- c(1,2) -->
<!-- d_prob = exp(as.matrix(X)%*%eta)/(1+exp(as.matrix(X)%*%eta)) -->
<!-- d_cat = rbinom(N,1,d_prob) -->

<!-- d_prob.0 = d_prob[d_cat==0] -->
<!-- d_prob.1 = d_prob[d_cat==1] -->


<!-- X.0 = X[d_cat==0,] -->
<!-- X.1 = X[d_cat==1,] -->


<!-- ## D -->
<!-- D <- list() -->
<!-- D$X <- rbind(X.0,X.1) -->
<!-- d_cat <- c(rep(0,nrow(X.0)),rep(1,nrow(X.1))) -->
<!-- D$d_cat <-  d_cat -->
<!-- D$d_prob <- c(d_prob.0, d_prob.1) -->

<!-- ``` -->

<!-- ##Simulation Start: -->

<!-- ###Initial var1 = var2 = 0.3, and correlation = 0 -->
<!-- ```{r initial1} -->
<!-- ## Omega -->
<!-- var <- c(1.2,0.8) -->
<!-- O = abs(diag(var,2)) -->
<!-- rho = 0.10 -->
<!-- O[1,2] <- rho*sqrt(var[1])*sqrt(var[2]) -->
<!-- O[2,1] <- O[1,2] -->
<!-- # o.r = O -->
<!-- # var1 <- abs(rnorm(1)) -->
<!-- # var2 <- abs(rnorm(1)) -->
<!-- # rho.r <- runif(1) -->

<!-- ## Control covariance matrix -->
<!-- rho.r <- rho -->
<!-- var1 <- var[1] -->
<!-- var2 <- var[2] -->

<!-- ## g.y -->
<!-- eps <- mvrnorm(n = N, c(0,0), O) -->
<!-- eps.0 = eps[d_cat==0] -->
<!-- eps.1 = eps[d_cat==1] -->

<!-- Y.0 = as.matrix(X.0)%*%B.0 + eps.0 -->
<!-- Y.1 = as.matrix(X.1)%*%B.1 + eps.1 -->


<!-- ## D -->
<!-- # D <- list() -->
<!-- # D$X <- rbind(X.0,X.1) -->
<!-- D$Y <- rbind(Y.0,Y.1) -->
<!-- # g.r<- D$X -->
<!--   # matrix(rep(0.5,N*k),nrow = N) -->
<!-- g.r <- D$Y-0.5 -->

<!-- ### Initial Values -->
<!-- eta.r <- rnorm(2) -->
<!-- # eta.r <- eta -->



<!-- print(iter) -->
<!-- res = c() -->
<!-- iter = 1 -->
<!-- res[iter] = 1000 -->
<!-- # theta.t = c(var1,var2, rho, c(B.0),c(B.0)) -->
<!-- # theta.r = c(runif(2,0,1), rep(0.1,9)) -->

<!-- theta.r = runif(3,0,1) -->
<!-- o.r = abs(diag(theta.r[c(1,2)],2)) -->
<!-- o.r[1,2] <- theta.r[3]*sqrt(theta.r[1])*sqrt(theta.r[2]) -->
<!-- o.r[2,1] <- o.r[1,2] -->

<!-- b.0.r <- matrix(rnorm(4),nrow = 2) -->
<!-- b.1.r <- matrix(rnorm(4),nrow = 2) -->
<!-- theta.r = c(theta.r, c(b.0.r), c(b.1.r)) -->
<!-- # b.0.r <- B.0 -->
<!-- # b.1.r <- B.1 -->


<!-- # res_eta = -0.01 -->

<!-- # b.0.r <- matrix(rnorm(4),2,2) -->
<!-- # b.1.r <- matrix(rnorm(4),2,2) -->

<!-- while(res[iter]>0.001){ -->
<!--   par_old = c(eta.r, theta.r) -->
<!--   print(iter) -->
<!--   # if(iter == 1){ -->
<!--     pi1.r = exp(as.matrix(D$X)%*%eta.r)/(1+exp(as.matrix(D$X)%*%eta.r)) -->
<!--     pi0.r = 1-pi1.r -->

<!--     p0.r = dmvnorm(g.r-as.matrix(D$X)%*%b.0.r,mean = c(0,0), sigma = o.r) -->
<!--     p1.r = dmvnorm(g.r-as.matrix(D$X)%*%b.1.r,mean = c(0,0), sigma = o.r) -->
<!--     P.r = (pi1.r*p1.r)/(pi1.r*p1.r+pi0.r*p0.r) -->
<!--     # res_eta = mean(abs(D$d_prob - P.r)) -->
<!--   # } -->


<!--   # label.new = ifelse(P.r>1-P.r,1,0) -->
<!--   # mean.0 = apply((g.r-as.matrix(D$X))[label.new==0,],2,mean) -->
<!--   # mean.1 = apply((g.r-as.matrix(D$X))[label.new==1,],2,mean) -->
<!--   #  -->
<!--   # P.r.cat = as.factor(ifelse(P.r>0.5,1,0)) -->
<!--   eta.r<- glm(P.r~.-1, data = D$X,family = binomial)$coef -->

<!--   sprintf("Estimated eta: %s", eta.r) -->
<!--   sprintf("True Estimated eta: %s", eta) -->

<!--   mytheta = function(par){ -->
<!--       o = matrix(0,2,2) -->
<!--       o[1,1]<-par[1] -->
<!--       o[2,2]<-par[2] -->
<!--       o[1,2] <- par[3]*prod(sqrt(diag(o))) -->
<!--       o[2,1] <- o[1,2] -->

<!--       beta1 <- par[4:5] -->
<!--       beta2 <- par[6:7] -->
<!--       b0 <- matrix(c(beta1,beta2),2) -->

<!--       beta1 <- par[8:9] -->
<!--       beta2 <- par[10:11] -->
<!--       b1 <- matrix(c(beta1,beta2),2) -->


<!--       o.det = prod(par[1],par[2])-o[1,2]^2 -->
<!--       o.det = det(o) -->
<!--       o.inv = matrix(0,2,2) -->
<!--       o.inv[1,1]<-par[2]/o.det -->
<!--       o.inv[2,2]<-par[1]/o.det -->
<!--       o.inv[1,2] <- -o[1,2]/o.det -->
<!--       o.inv[2,1] <- -o[2,1]/o.det -->
<!--       # o.inv = solve(o) -->
<!--       # sum(c(log(P.r))*(-0.5)*c(apply(as.matrix(g.r)-as.matrix(D$X)%*%b1,1,function(x) t(as.matrix(x))%*%o.inv%*%as.matrix(x))), -->
<!--       #     c(1-log(P.r))*(-0.5)*c(pply(as.matrix(g.r)-as.matrix(D$X)%*%b0,1,function(x) t(as.matrix(x))%*%o.inv%*%as.matrix(x))), -->
<!--       #     -N/2*log(o.det) -->
<!--       sum( -->
<!--         P.r*-0.5*c(apply(as.matrix(g.r)-as.matrix(D$X)%*%b1,1,function(x) t(as.matrix(x))%*%o.inv%*%as.matrix(x))) -->
<!--           , -->
<!--           (1-P.r)*-0.5*c(apply(as.matrix(g.r)-as.matrix(D$X)%*%b0,1,function(x) t(as.matrix(x))%*%o.inv%*%as.matrix(x))) -->
<!--          ,-N/2*log(o.det)) -->
<!--   } -->
<!--   result = try(optim(theta.r,mytheta, method = 'BFGS', -->
<!--                     control= list(fnscale=-1))) -->


<!--   if(inherits(result, "try-error")==TRUE){ -->
<!--     res = res -->
<!--     result2.1 = try(pava(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,1],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,1],nrow=2)))) -->
<!--                     +0.5*(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,2],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,2],nrow=2)))) -->
<!--                     -g.r[,2])*o.inv[1,2]/o.inv[1,1])) -->


<!--     result2.2 = try(pava(diag(as.matrix(D$X)%*%as.matrix(apply(1-P.r,1, function(x) (1-x)*as.matrix(b.0.r[,2],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,2],nrow=2)))) -->
<!--   +0.5*(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,1],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,1],nrow=2)))) -->
<!--         -g.r[,1])*o.inv[1,2]/o.inv[2,2])) -->

<!--     if(inherits(result2.1, "try-error")==TRUE | inherits(result2.2, "try-error")==TRUE){ -->
<!--       res = res -->
<!--     }else{ -->
<!--       g.r.1 <- matrix(0, nrow = 1000, ncol = 2) -->
<!--       g.r.1[,1] <- pava(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,1],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,1],nrow=2)))) -->
<!--                     +0.5*(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,2],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,2],nrow=2)))) -->
<!--                     -g.r[,2])*o.inv[1,2]/o.inv[1,1]) -->


<!--       g.r.1[,2] <- pava(diag(as.matrix(D$X)%*%as.matrix(apply(1-P.r,1, function(x) (1-x)*as.matrix(b.0.r[,2],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,2],nrow=2)))) -->
<!--   +0.5*(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,1],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,1],nrow=2)))) -->
<!--         -g.r[,1])*o.inv[1,2]/o.inv[2,2]) -->
<!--     g.r <- g.r.1 -->
<!--     } -->
<!--   }else{ -->
<!--     theta.opt = optim(theta.r,mytheta, method = 'BFGS', -->
<!--                     control= list(fnscale=-1)) -->
<!--     theta.r <- theta.opt$par -->
<!--   theta.conv <- theta.opt$convergence -->
<!--   print(ifelse(theta.conv==0,'success','fail')) -->
<!--   sprintf("Estimated theta: %s, %s and %s ", theta.r[1],theta.r[2], theta.r[3]) -->
<!--   sprintf("True theta: %s, %s and %s", O[1,1],O[2,2], rho) -->
<!--   #  -->
<!--   # sprintf("Estimated beta0: %s, %s, %s,%s", -->
<!--   #         theta.r[4],theta.r[5],theta.r[6],theta.r[7]) -->
<!--   #  -->
<!--   # sprintf("True beta0: %s, %s, %s,%s", -->
<!--   #        B.0[1],B.0[2],B.0[3],B.0[4]) -->
<!--   #  -->
<!--   # sprintf("Estimated beta1: %s, %s, %s,%s ", -->
<!--   #        theta.r[8],theta.r[9],theta.r[10],theta.r[11]) -->
<!--   #  -->
<!--   # sprintf("True beta1: %s, %s, %s,%s", -->
<!--   #        B.1[1],B.1[2],B.1[3],B.1[4]) -->

<!--   b.0.r = matrix(theta.r[4:7],2,2) -->
<!--   b.1.r = matrix(theta.r[8:11],2,2) -->

<!--   o.r = matrix(0,2,2) -->
<!--   o.r[1,1]<-theta.r[1] -->
<!--   o.r[2,2]<-theta.r[2] -->
<!--   o.r[1,2] <- par[3]*prod(sqrt(diag(o.r))) -->
<!--   o.r[2,1] <- o.r[1,2] -->
<!--   o.det = prod(diag(o.r))-o.r[1,2]^2 -->
<!--   o.inv = matrix(0,2,2) -->
<!--   o.inv[1,1]<-o.r[2,2]/o.det -->
<!--   o.inv[2,2]<-o.r[1,1]/o.det -->
<!--   o.inv[1,2] <- -o.r[2,1]/o.det -->
<!--   o.inv[2,1] <- -o.r[2,1]/o.det -->

<!--   g.r.1 <- matrix(0, nrow = 1000, ncol = 2) -->
<!--   g.r.1[,1] <- pava(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,1],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,1],nrow=2)))) -->
<!--                     +0.5*(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,2],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,2],nrow=2)))) -->
<!--                     -g.r[,2])*o.inv[1,2]/o.inv[1,1]) -->

<!--   g.r.1[,2] <-  pava(diag(as.matrix(D$X)%*%as.matrix(apply(1-P.r,1, function(x) (1-x)*as.matrix(b.0.r[,2],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,2],nrow=2)))) -->
<!--   +0.5*(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,1],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,1],nrow=2)))) -->
<!--         -g.r[,1])*o.inv[1,2]/o.inv[2,2]) -->

<!--   res2 = mean(abs(g.r-g.r.1)) -->
<!--   g.r <- g.r.1 -->
<!--   # res[iter] = mean(abs(g.r-D$Y)) -->
<!--    par_new = c(eta.r, theta.r) -->

<!--    # par_new = c(res_eta, theta.r) -->
<!--   # res = append(res, max(abs(par_old-par_new)), after = length(res)) -->
<!--   res = append(res,max(res2,abs(par_old-par_new)), after = length(res)) -->
<!--   # g.r <- g.r.1 -->
<!--   print(res[iter]) -->
<!--   iter = iter+1 -->
<!--   } -->
<!-- } -->


<!-- mean(as.matrix(D$X[P.r<0.5,])%*%B.0 - D$Y[P.r<0.5,]) -->


<!-- sprintf("Converge in %s iteration:", iter) -->
<!-- print("Converge covariance matrix: ") -->
<!-- print(o.r) -->

<!-- print("Original covariance matrix: ") -->
<!-- print(O) -->

<!-- ``` -->
<!-- ###Initial var1 = var2 = 0.3, and correlation = 0.1 -->
<!-- ```{r initial2} -->
<!-- iter = 1 -->
<!-- res=0 -->
<!-- var1 = 0.3 -->
<!-- var2 = 0.3 -->
<!-- rho = 0.1 -->

<!-- var <- c(var1,var2) -->
<!-- O = abs(diag(var,2)) -->
<!-- O[1,2] <- rho*prod(sqrt(diag(O))) -->
<!-- O[2,1] <- O[1,2] -->
<!-- o.r = O -->


<!-- ### Initial Values -->

<!-- eta.r <- c(1,2) -->

<!-- # var1 <- abs(rnorm(1)) -->
<!-- # var2 <- abs(rnorm(1)) -->
<!-- # rho.r <- runif(1) -->

<!-- ## Control covariance matrix -->
<!-- rho.r <- rho -->
<!-- var1 <- var[1] -->
<!-- var2 <- var[2] -->


<!-- g.r<-matrix(rnorm(N*k),nrow = N) -->
<!-- # g.r <- log(D$Y) -->
<!-- # b.0.r <- matrix(rnorm(4),nrow = 2) -->
<!-- # b.1.r <- matrix(rnorm(4),nrow = 2) -->
<!-- b.0.r <- B.0 -->
<!-- b.1.r <- B.1 -->



<!-- ``` -->


<!-- ```{r simulation2} -->
<!-- print(iter) -->
<!-- iter = 1 -->
<!-- res[iter] = 100 -->

<!-- while(res[iter]>0.01){ -->
<!--   print(iter) -->
<!--   pi1.r = exp(as.matrix(D$X)%*%eta.r)/(1+exp(as.matrix(D$X)%*%eta.r)) -->
<!--   pi0.r = 1-pi1.r -->

<!--   p0.r = dmvnorm(g.r-as.matrix(D$X)%*%b.0.r,mean = c(0,0), sigma = o.r) -->
<!--   p1.r = dmvnorm(g.r-as.matrix(D$X)%*%b.1.r,mean = c(0,0), sigma = o.r) -->

<!--   P.r = (pi1.r*p1.r)/(pi1.r*p1.r+pi0.r*p0.r) -->
<!--   eta.r<- glm(P.r~.-1, data = D$X,family = binomial)$coef -->
<!--   sprintf("Estimated eta: %s", eta.r) -->

<!--   label.new = ifelse(P.r>1-P.r,1,0) -->

<!--   theta.r <- optim( -->
<!--     c(c(b.0.r),c(b.1.r),var1,var2,rho), -->
<!--     function(par){ -->
<!--       b0 = matrix(par[1:4], 2, 2) # Reshape -->
<!--       b1 = matrix(par[5:8], 2, 2) # Reshape -->
<!--       o = matrix(0,2,2) -->
<!--       o[1,1]<-par[9] -->
<!--       o[2,2]<-par[10] -->
<!--       o[1,2] <- par[11]*prod(sqrt(diag(o))) -->
<!--       o[2,1] <- o[1,2] -->

<!--       o.det = prod(par[10],par[9])-par[11]^2 -->
<!--       o.inv = matrix(0,2,2) -->
<!--       o.inv[1,1]<-par[10]/o.det -->
<!--       o.inv[2,2]<-par[9]/o.det -->
<!--       o.inv[1,2] <- -par[11]/o.det -->
<!--       o.inv[2,1] <- -par[11]/o.det -->

<!--       sum(c(P.r)*(-0.5)*c(apply(as.matrix(g.r)-as.matrix(D$X)%*%b1,1,function(x) t(as.matrix(x))%*%o.inv%*%as.matrix(x))), -->
<!--           c(1- P.r)*(-0.5)*c(apply(as.matrix(g.r)-as.matrix(D$X)%*%b0,1,function(x) t(as.matrix(x))%*%o.inv%*%as.matrix(x))), -->
<!--           -N/2*log(o.det)) -->
<!--     } -->
<!--   )$par -->

<!--   b.0.r = matrix(theta.r[1:4],2,2) -->
<!--   b.1.r = matrix(theta.r[5:8],2,2) -->
<!--   o.r = matrix(0,2,2) -->
<!--   o.r[1,1]<-theta.r[9] -->
<!--   o.r[2,2]<-theta.r[10] -->
<!--   o.r[1,2] <- theta.r[11]*prod(sqrt(diag(o.r))) -->
<!--   o.r[2,1] <- o.r[1,2] -->

<!--   # o.1.r = matrix(theta.r[13:16],2,2) -->
<!--    o.det = prod(sqrt(diag(o.r)))-o.r[1,2]^2 -->
<!--    o.inv = matrix(0,2,2) -->
<!--    o.inv[1,1]<-o.r[2,2]/o.det -->
<!--    o.inv[2,2]<-o.r[1,1]/o.det -->
<!--    o.inv[1,2] <- -o.r[2,1]/o.det -->
<!--    o.inv[2,1] <- -o.r[2,1]/o.det -->

<!--   g.r.1 <- matrix(0,nrow = 1000, ncol = 2) -->
<!--   g.r.1[,1] <- pava(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,1],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,1],nrow=2)))) -->
<!--                     +0.5*(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,2],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,2],nrow=2)))) -->
<!--                           -g.r[,2])*o.inv[1,2]/o.inv[1,1]) -->

<!--   g.r.1[,2] <-  pava(diag(as.matrix(D$X)%*%as.matrix(apply(1-P.r,1, function(x) (1-x)*as.matrix(b.0.r[,2],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,2],nrow=2)))) -->
<!--   +0.5*(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,1],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,1],nrow=2)))) -->
<!--         -g.r[,1])*o.inv[1,2]/o.inv[2,2]) -->

<!--   g.r <- g.r.1 -->

<!--   res = (abs(o.r[1,1]-var1)<0.01)*((abs(o.r[2,2]-var2)<0.01))*(abs(o.r[1,2]-rho)<0.01) -->
<!--   print(res) -->
<!--   iter = iter+1 -->
<!--   if(iter >= 50) break -->

<!-- } -->

<!-- sprintf("Converge in %s iteration:", iter) -->
<!-- print("Converge covariance matrix: ") -->
<!-- print(o.r) -->

<!-- print("Original covariance matrix: ") -->
<!-- print(O) -->

<!-- ``` -->


<!-- ###Initial var1 = 0.1 var2 = 0.4, and correlation = 0 -->
<!-- ```{r initial3} -->
<!-- iter = 1 -->
<!-- res=0 -->
<!-- var1 = 0.1 -->
<!-- var2 = 0.4 -->
<!-- rho = 0 -->

<!-- var <- c(var1,var2) -->
<!-- O = abs(diag(var,2)) -->
<!-- rho = 0 -->
<!-- O[1,2] <- rho*prod(sqrt(diag(O))) -->
<!-- O[2,1] <- O[1,2] -->
<!-- o.r = O -->


<!-- ### Initial Values -->

<!-- eta.r <- c(1,2) -->

<!-- # var1 <- abs(rnorm(1)) -->
<!-- # var2 <- abs(rnorm(1)) -->
<!-- # rho.r <- runif(1) -->

<!-- ## Control covariance matrix -->
<!-- rho.r <- rho -->
<!-- var1 <- var[1] -->
<!-- var2 <- var[2] -->


<!-- # g.r<-matrix(rnorm(N*k),nrow = N) -->
<!-- g.r <- log(D$Y) -->
<!-- # b.0.r <- matrix(rnorm(4),nrow = 2) -->
<!-- # b.1.r <- matrix(rnorm(4),nrow = 2) -->
<!-- b.0.r <- B.0 -->
<!-- b.1.r <- B.1 -->



<!-- ``` -->


<!-- ```{r simulation3} -->
<!-- print(iter) -->
<!-- while(res == 0 |is.null(res)){ -->
<!--   print(iter) -->
<!--   pi1.r = exp(as.matrix(D$X)%*%eta.r)/(1+exp(as.matrix(D$X)%*%eta.r)) -->
<!--   pi0.r = 1-pi1.r -->

<!--   p0.r = dmvnorm(g.r-as.matrix(D$X)%*%b.0.r,mean = mean.0, sigma = o.r) -->
<!--   p1.r = dmvnorm(g.r-as.matrix(D$X)%*%b.1.r,mean = mean.1, sigma = o.r) -->

<!--   P.r = (pi1.r*p1.r)/(pi1.r*p1.r+pi0.r*p0.r) -->
<!--   eta.r<- glm(P.r~.-1, data = D$X,family = binomial)$coef -->
<!--   sprintf("Estimated eta: %s", eta.r) -->

<!--   label.new = ifelse(P.r>1-P.r,1,0) -->
<!--   # mean.0 = apply((g.r-as.matrix(D$X))[label.new==0,],2,mean) -->
<!--   # mean.1 = apply((g.r-as.matrix(D$X))[label.new==1,],2,mean) -->
<!--   #  -->
<!--   #  -->

<!--   theta.r <- optim( -->
<!--     c(c(b.0.r),c(b.1.r),var1,var2,rho), -->
<!--     function(par){ -->
<!--       b0 = matrix(par[1:4], 2, 2) # Reshape -->
<!--       b1 = matrix(par[5:8], 2, 2) # Reshape -->
<!--       o = matrix(0,2,2) -->
<!--       o[1,1]<-par[9] -->
<!--       o[2,2]<-par[10] -->
<!--       o[1,2] <- par[11]*prod(sqrt(diag(o))) -->
<!--       o[2,1] <- o[1,2] -->

<!--       o.det = prod(par[10],par[9])-par[11]^2 -->
<!--       o.inv = matrix(0,2,2) -->
<!--       o.inv[1,1]<-par[10]/o.det -->
<!--       o.inv[2,2]<-par[9]/o.det -->
<!--       o.inv[1,2] <- -par[11]/o.det -->
<!--       o.inv[2,1] <- -par[11]/o.det -->

<!--       sum(c(P.r)*(-0.5)*c(apply(as.matrix(g.r)-as.matrix(D$X)%*%b1,1,function(x) t(as.matrix(x))%*%o.inv%*%as.matrix(x))), -->
<!--           c(1- P.r)*(-0.5)*c(apply(as.matrix(g.r)-as.matrix(D$X)%*%b0,1,function(x) t(as.matrix(x))%*%o.inv%*%as.matrix(x))), -->
<!--           -N/2*log(o.det)) -->
<!--     } -->
<!--   )$par -->

<!--   b.0.r = matrix(theta.r[1:4],2,2) -->
<!--   b.1.r = matrix(theta.r[5:8],2,2) -->
<!--   o.r = matrix(0,2,2) -->
<!--   o.r[1,1]<-theta.r[9] -->
<!--   o.r[2,2]<-theta.r[10] -->
<!--   o.r[1,2] <- theta.r[11]*prod(sqrt(diag(o.r))) -->
<!--   o.r[2,1] <- o.r[1,2] -->

<!--   # b.0.r -->
<!--   # B.0 -->
<!--   #  -->
<!--   # b.1.r -->
<!--   # B.1 -->
<!--   #  -->
<!--   # theta.r[9] -->
<!--   # var1 -->
<!--   #  -->
<!--   # theta.r[10] -->
<!--   # var2 -->
<!--   #  -->
<!--   # theta.r[11] -->
<!--   # rho -->




<!--   # o.1.r = matrix(theta.r[13:16],2,2) -->
<!--    o.det = prod(sqrt(diag(o.r)))-o.r[1,2]^2 -->
<!--    o.inv = matrix(0,2,2) -->
<!--    o.inv[1,1]<-o.r[2,2]/o.det -->
<!--    o.inv[2,2]<-o.r[1,1]/o.det -->
<!--    o.inv[1,2] <- -o.r[2,1]/o.det -->
<!--    o.inv[2,1] <- -o.r[2,1]/o.det -->

<!--   g.r.1 <- matrix(0,nrow = 1000, ncol = 2) -->
<!--   g.r.1[,1] <- pava(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,1],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,1],nrow=2)))) -->
<!--                     +0.5*(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,2],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,2],nrow=2)))) -->
<!--                           -g.r[,2])*o.inv[1,2]/o.inv[1,1]) -->

<!--   g.r.1[,2] <-  pava(diag(as.matrix(D$X)%*%as.matrix(apply(1-P.r,1, function(x) (1-x)*as.matrix(b.0.r[,2],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,2],nrow=2)))) -->
<!--   +0.5*(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,1],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,1],nrow=2)))) -->
<!--         -g.r[,1])*o.inv[1,2]/o.inv[2,2]) -->

<!--   g.r <- g.r.1 -->

<!--   res = (abs(o.r[1,1]-var1)<0.01)*((abs(o.r[2,2]-var2)<0.01))*(abs(o.r[1,2]-rho)<0.01) -->
<!--   print(res) -->
<!--   iter = iter+1 -->
<!--   if(iter >= 5) break -->

<!-- } -->

<!-- sprintf("Converge in %s iteration:", iter) -->
<!-- print("Converge covariance matrix: ") -->
<!-- print(o.r) -->

<!-- print("Original covariance matrix: ") -->
<!-- print(O) -->

<!-- ``` -->


<!-- ###Initial var1 = 0.1 var2 = 0.4, and correlation = 0.1 -->
<!-- ```{r initial4} -->
<!-- iter = 1 -->
<!-- res=0 -->
<!-- var1 = 0.1 -->
<!-- var2 = 0.4 -->
<!-- rho = 0.1 -->

<!-- var <- c(var1,var2) -->
<!-- O = abs(diag(var,2)) -->
<!-- rho = 0 -->
<!-- O[1,2] <- rho*prod(sqrt(diag(O))) -->
<!-- O[2,1] <- O[1,2] -->
<!-- o.r = O -->


<!-- ### Initial Values -->

<!-- eta.r <- c(1,2) -->

<!-- # var1 <- abs(rnorm(1)) -->
<!-- # var2 <- abs(rnorm(1)) -->
<!-- # rho.r <- runif(1) -->

<!-- ## Control covariance matrix -->
<!-- rho.r <- rho -->
<!-- var1 <- var[1] -->
<!-- var2 <- var[2] -->


<!-- # g.r<-matrix(rnorm(N*k),nrow = N) -->
<!-- g.r <- log(D$Y) -->
<!-- # b.0.r <- matrix(rnorm(4),nrow = 2) -->
<!-- # b.1.r <- matrix(rnorm(4),nrow = 2) -->
<!-- b.0.r <- B.0 -->
<!-- b.1.r <- B.1 -->


<!-- ``` -->


<!-- ```{r simulation4} -->
<!-- print(iter) -->
<!-- while(res == 0 |is.null(res)){ -->
<!--   print(iter) -->
<!--   pi1.r = exp(as.matrix(D$X)%*%eta.r)/(1+exp(as.matrix(D$X)%*%eta.r)) -->
<!--   pi0.r = 1-pi1.r -->

<!--   p0.r = dmvnorm(g.r-as.matrix(D$X)%*%b.0.r,mean = mean.0, sigma = o.r) -->
<!--   p1.r = dmvnorm(g.r-as.matrix(D$X)%*%b.1.r,mean = mean.1, sigma = o.r) -->

<!--   P.r = (pi1.r*p1.r)/(pi1.r*p1.r+pi0.r*p0.r) -->
<!--   eta.r<- glm(P.r~.-1, data = D$X,family = binomial)$coef -->
<!--   sprintf("Estimated eta: %s", eta.r) -->

<!--   label.new = ifelse(P.r>1-P.r,1,0) -->
<!--   # mean.0 = apply((g.r-as.matrix(D$X))[label.new==0,],2,mean) -->
<!--   # mean.1 = apply((g.r-as.matrix(D$X))[label.new==1,],2,mean) -->
<!--   #  -->
<!--   #  -->

<!--   theta.r <- optim( -->
<!--     c(c(b.0.r),c(b.1.r),var1,var2,rho), -->
<!--     function(par){ -->
<!--       b0 = matrix(par[1:4], 2, 2) # Reshape -->
<!--       b1 = matrix(par[5:8], 2, 2) # Reshape -->
<!--       o = matrix(0,2,2) -->
<!--       o[1,1]<-par[9] -->
<!--       o[2,2]<-par[10] -->
<!--       o[1,2] <- par[11]*prod(sqrt(diag(o))) -->
<!--       o[2,1] <- o[1,2] -->

<!--       o.det = prod(par[10],par[9])-par[11]^2 -->
<!--       o.inv = matrix(0,2,2) -->
<!--       o.inv[1,1]<-par[10]/o.det -->
<!--       o.inv[2,2]<-par[9]/o.det -->
<!--       o.inv[1,2] <- -par[11]/o.det -->
<!--       o.inv[2,1] <- -par[11]/o.det -->

<!--       sum(c(P.r)*(-0.5)*c(apply(as.matrix(g.r)-as.matrix(D$X)%*%b1,1,function(x) t(as.matrix(x))%*%o.inv%*%as.matrix(x))), -->
<!--           c(1- P.r)*(-0.5)*c(apply(as.matrix(g.r)-as.matrix(D$X)%*%b0,1,function(x) t(as.matrix(x))%*%o.inv%*%as.matrix(x))), -->
<!--           -N/2*log(o.det)) -->
<!--     } -->
<!--   )$par -->

<!--   b.0.r = matrix(theta.r[1:4],2,2) -->
<!--   b.1.r = matrix(theta.r[5:8],2,2) -->
<!--   o.r = matrix(0,2,2) -->
<!--   o.r[1,1]<-theta.r[9] -->
<!--   o.r[2,2]<-theta.r[10] -->
<!--   o.r[1,2] <- theta.r[11]*prod(sqrt(diag(o.r))) -->
<!--   o.r[2,1] <- o.r[1,2] -->

<!--   # b.0.r -->
<!--   # B.0 -->
<!--   #  -->
<!--   # b.1.r -->
<!--   # B.1 -->
<!--   #  -->
<!--   # theta.r[9] -->
<!--   # var1 -->
<!--   #  -->
<!--   # theta.r[10] -->
<!--   # var2 -->
<!--   #  -->
<!--   # theta.r[11] -->
<!--   # rho -->




<!--   # o.1.r = matrix(theta.r[13:16],2,2) -->
<!--    o.det = prod(sqrt(diag(o.r)))-o.r[1,2]^2 -->
<!--    o.inv = matrix(0,2,2) -->
<!--    o.inv[1,1]<-o.r[2,2]/o.det -->
<!--    o.inv[2,2]<-o.r[1,1]/o.det -->
<!--    o.inv[1,2] <- -o.r[2,1]/o.det -->
<!--    o.inv[2,1] <- -o.r[2,1]/o.det -->

<!--   g.r.1 <- matrix(0,nrow = 1000, ncol = 2) -->
<!--   g.r.1[,1] <- pava(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,1],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,1],nrow=2)))) -->
<!--                     +0.5*(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,2],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,2],nrow=2)))) -->
<!--                           -g.r[,2])*o.inv[1,2]/o.inv[1,1]) -->

<!--   g.r.1[,2] <-  pava(diag(as.matrix(D$X)%*%as.matrix(apply(1-P.r,1, function(x) (1-x)*as.matrix(b.0.r[,2],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,2],nrow=2)))) -->
<!--   +0.5*(diag(as.matrix(D$X)%*%as.matrix(apply(P.r,1, function(x) (1-x)*as.matrix(b.0.r[,1],nrow=2))+apply(P.r,1, function(x) x*as.matrix(b.1.r[,1],nrow=2)))) -->
<!--         -g.r[,1])*o.inv[1,2]/o.inv[2,2]) -->

<!--   g.r <- g.r.1 -->

<!--   res = (abs(o.r[1,1]-var1)<0.1)*((abs(o.r[2,2]-var2)<0.1))*(abs(o.r[1,2]-rho)<0.1) -->
<!--   print(res) -->
<!--   iter = iter+1 -->
<!--   if(iter >= 5) break -->

<!-- } -->

<!-- sprintf("Converge in %s iteration:", iter) -->
<!-- print("Converge covariance matrix: ") -->
<!-- print(o.r) -->

<!-- print("Original covariance matrix: ") -->
<!-- print(O) -->

<!-- ``` -->





